Mining Scenario/Transaction Pairs in HW/SW Co-verification Using Symbolic Execution

### 2017-04-05 paper.tex
psl

\textbf{Step 4: Property Driven Slicing of Co-verification Model}
A property-driven slicing is performed on the unified model, $\mathcal{M}_{seq}$.  
This step is purely syntactic, meaning that we perform a backward dependency 
analysis starting from the property which only preserve those 
program fragments that are relevant to a given property. The sliced program 
is then passed to the symbolic execution engine for path-based exploration. \\
%
%=======================================================================================
%\subsection{\verifox: Path-wise Symbolic Execution Tool} 
%=======================================================================================
\input{verifox}
%
\subsection{Approach 2: Monolithic Co-verification Technique}
%
\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.6]{figures/traditional_flow.pdf}
\caption{Conventional HW/SW Co-verification Flow}
\label{fig:conventional}
\end{center}
\end{figure}
%
Figure~\ref{fig:conventional} illustrates the conventional approach to HW/SW
co-veri\-fi\-cation, as implemented in the state-of-the-art co-verification
tool, \hwcbmcv~\cite{CKY03,vlsid13}.  \hwcbmcv is the only open-source
formal co-verification tool that supports Verilog RTL (System Verilog 2009
standard) and C/C++ firmware.  In contrast to our proposed approach,
\hwcbmcv maintains two separate flows for HW and FW.  The top flow in
Figure~\ref{fig:conventional} uses synthesis to obtain either a bit-level or
a word-level netlist from Verilog RTL.  The bottom flow illustrates the
translation of the C program into static single assignment (SSA) form. 
These two flows meet only at the solver.  Thus, \hwcbmcv generates a
monolithic formula from the C and RTL description, which is then checked
with SAT/SMT solvers.  \hwcbmcv provides specific handshake primitives such
as $next\_timeframe()$ and $set\_inputs()$ to model FW-HW communications.
\rmcmt{
To this end, \hwcbmcv constructs a co-verification model through 
in tandem symbolic execution of the HW and FW models.  A bit-level 
netlist representation in And Inverter Graph (AIG) format or word-level netlist in
format similar to SMT-LIB standards is synthesized from a HW Register Transfer 
Level (RTL) implementation. Similarly, the SW, given in C, is automatically 
translated into a Static Single Assignment (SSA) form.  A monolithic verification 
condition is generated from these two models which is then solved using a 
}
%
\Omit{
The hardware and firmware run independently of each other. 
The communication between them takes place through these function calls. 
}
%===============================================================================
\section{Experimental Results}
%===============================================================================
%
We report experimental results for FW-HW co-verification of a UART IP and a
SoC design.  All our experiments were performed on an Intel Xeon 3.07\,GHz
machine with 48\,GB RAM.  All times reported are in seconds.  The timeout 
for all our experiments was set to 2~hours.  
%

@@

% ===============================================================================
\section{Limitations of Proposed Approach}
% ===============================================================================

>>>>

\textbf{Step 4: Property Driven Slicing of Co-verification Model}
A property-driven slicing is performed on the unified model, $\mathcal{M}_{seq}$.  
This step is purely syntactic, meaning that we perform a backward dependency 
analysis starting from the property which only preserve those 
program fragments that are relevant to a given property. The sliced program 
is then passed to the symbolic execution engine for path-based exploration. \\
%
%=======================================================================================
%\subsection{\verifox: Path-wise Symbolic Execution Tool} 
%=======================================================================================
\input{verifox}
%
\subsection{Approach 2: Monolithic Co-verification Technique}
%
\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.6]{figures/traditional_flow.pdf}
\caption{Conventional HW/SW Co-verification Flow}
\label{fig:conventional}
\end{center}
\end{figure}
%
Figure~\ref{fig:conventional} illustrates the conventional approach to HW/SW
co-veri\-fi\-cation, as implemented in the state-of-the-art co-verification
tool, \hwcbmcv~\cite{CKY03,vlsid13}.  \hwcbmcv is the only open-source
formal co-verification tool that supports Verilog RTL (System Verilog 2009
standard) and C/C++ firmware.  In contrast to our proposed approach,
\hwcbmcv maintains two separate flows for HW and FW.  The top flow in
Figure~\ref{fig:conventional} uses synthesis to obtain either a bit-level or
a word-level netlist from Verilog RTL.  The bottom flow illustrates the
translation of the C program into static single assignment (SSA) form. 
These two flows meet only at the solver.  Thus, \hwcbmcv generates a
monolithic formula from the C and RTL description, which is then checked
with SAT/SMT solvers.  \hwcbmcv provides specific handshake primitives such
as $next\_timeframe()$ and $set\_inputs()$ to model FW-HW communications.
\rmcmt{
To this end, \hwcbmcv constructs a co-verification model through 
in tandem symbolic execution of the HW and FW models.  A bit-level 
netlist representation in And Inverter Graph (AIG) format or word-level netlist in
format similar to SMT-LIB standards is synthesized from a HW Register Transfer 
Level (RTL) implementation. Similarly, the SW, given in C, is automatically 
translated into a Static Single Assignment (SSA) form.  A monolithic verification 
condition is generated from these two models which is then solved using a 
}
%
\Omit{
The hardware and firmware run independently of each other. 
The communication between them takes place through these function calls. 
}
%===============================================================================
\section{Property Specification for Co-verification}
%===============================================================================
Lack of support for property specification in a HW/SW co-design is one of the
stumbling blocks for the application of formal techniques in co-verification.  
In this paper, we express a co-design property in C 
with the support of special primitive, called {\em next\_timeframe()}, 
that can express temporal correlation between HW and FW events. 
In this paper, we classify co-design properties into two 
classes -- {\em transaction-level} property and {\em component-level} property.
%-------------------------------------------------------------------------------
\subsection{Transaction-level Property}
%-------------------------------------------------------------------------------
A {\em Transaction-level} property ($\psi_{t}$) formally captures the 
design intent of the interaction between a $\mathcal{ST}$ and $\mathcal{HT}$, 
that is, it is defined at the transaction boundaries.  
Recall that a $\mathcal{ST}$ is a service in response to some external environment 
or HW interrupts (for example acknowledgement or exceptions). Similarly, 
$\mathcal{HT}$ is a finite-length service in response to some SW events or 
other HW events.

Thus, a transaction-level property follows implication structure -- the 
antecedent of the implication is an event in $\mathcal{ST}$ or 
$\mathcal{HT}$ and the consequent is an event in $\mathcal{HT}$ 
or $\mathcal{ST}$ respectively.  An event in $\mathcal{ST}$ may be 
a function call or an update to program variables. Similarly, an event in 
$\mathcal{HT}$ corresponds to an update of combinational or sequential 
elements. \rmcmt{example}

%-------------------------------------------------------------------------------
\subsection{Component-level Property}
%-------------------------------------------------------------------------------
A {\em component-level} property ($\psi_{c}$) is defined purely at the 
level of individual components of a co-design system. Recall that a component 
may be a HW model, a SW model or an interface model which contains only the 
interface logic.  A component-level property captures the design intent of a 
component in terms of its input/output behaviors.  This type of property 
is useful in a co-design environment for verifying individual components.   
Note that unlike the structure of $\psi_{t}$ which requires the antecedent 
or consequent to be a HW or SW event,  $\psi_{c}$ only contains signals 
(ports) or variables of a particular component. \rmcmt{example}

%===============================================================================
\section{Experimental Results}
%===============================================================================
%
We report experimental results for FW-HW co-verification of a UART IP and a
SoC design.  All our experiments were performed on an Intel Xeon 3.07\,GHz
machine with 48\,GB RAM.  All times reported are in seconds.  The timeout 
for all our experiments was set to 2~hours.  
%

@@

% ===============================================================================
\section{Limitations of Proposed Approach}
% ===============================================================================
The primary motivation for constructing a sequential single threaded unified 
co-verification model is to avoid enumerating exponential number of interleavings 
between the HW and FW threads.  We have shown that this is extremely beneficial for 
co-designs that exhibits producer-consumer relationship.  To this end, we construct 
a sequential co-verification model in \verifox through appropriate composition of 
HW and FW threads.  Our path-based algorithm in \verifox is able to suitably exploit 
this interaction behavior in a sequential co-verification model through symbolic 
execution by generating relevant scenario/transaction pairs.  However, this approach 
is not applicable for co-designs that exhibits true concurrency~\cite{concurrency}, 
that is, a FW its interacting HW threads does not show producer-consumer relationship.
